Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-06 programlogic.tex
+

In the rest of this, we explain how specifications of some selected \textsf{AMD64} instructions look like under the decisions made on the reasoning principles.
\begin{figure} 
  \[
  \begin{array}{l}
    \textsf{wpd\_def e s E1 } \Phi \;\mathsf{ cr3val } : \textsf{iProp }\Sigma := \\
   \qquad ((\textsf{cr cr3}) \mapsto_{\textsf{r}} (\textsf{num cr3val)}) \textsf{ cr3val}) \ast (\Phi \textsf{ cr3val}) \wand \textsf{WP e E } @ \textsf{s ; E1 } \{\{\_, \textsf{True} \}\}
    \end{array}
  \]
\caption{Unfolded Hoare-Double Definition for \textsf{vProp} Logic }
\label{fig:wpddefinition}
\end{figure}

@@

\inferrule[WriteToRegFromReg]{

@@

\inferrule[WriteToPhysMemFromReg]{

@@

\inferrule[WriteToRegFromPhysMem]{

@@

\inferrule[WriteToRegFromVirtMem]{
  \{P \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}\;\overline{is}

@@

  \{P \ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}

@@

\inferrule[WriteToVirtMemFromReg]{
  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{rvs}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}\;\overline{ is}  

@@

  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{rvs}   \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{rvs} \}

@@

\inferrule[WriteToRegCtlFromReg]{

@@

\inferrule[WriteToRegFromRegCtl]{

>>>>

In the rest of this, we explain how specifications of some selected \textsf{AMD64} instructions look like under the decisions made on the reasoning principles. All rules, e.g. the ones with different addressing mode, can be found in our artifact.

In the general outline of the proof in Figure \ref{wpdamd}, we see that each rule annotated with an address value ($\{\rtv\}$), i.e. a root address of an address-space, under which the resources mentioned in the specification are valid. Moreover, there is a frame resource $P$ in each rule.
\begin{figure} 
  \[
  \begin{array}{l}
    \textsf{wpd\_def e s E1 } \Phi \;\mathsf{ cr3val } : \textsf{iProp }\Sigma := \\
   \qquad ((\textsf{cr cr3}) \mapsto_{\textsf{r}} (\textsf{num cr3val)}) \textsf{ cr3val}) \ast (\Phi \textsf{ cr3val}) \wand \textsf{WP e E } @ \textsf{s ; E1 } \{\{\_, \textsf{True} \}\}
    \end{array}
  \]
\caption{Unfolded Hoare-Double Definition for \textsf{vProp} Logic }
\label{fig:wpddefinition}
\end{figure}

@@

  \inferrule[WriteToRegFromReg | \{\textsf{rtv}\}]{

@@

\inferrule[WriteToPhysMemFromReg | \{\textsf{rtv}\}]{

@@

\inferrule[WriteToRegFromPhysMem | \{\textsf{rtv}\}]{

@@

\inferrule[WriteToRegFromVirtMem | \{\textsf{rtv}\}]{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast \mathcal{I}\textsf{ASpace} \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}\;\overline{is}

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}

@@

\inferrule[WriteToVirtMemFromReg | \{\textsf{rtv}\}]{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_s \mapsto_{r}\{q\}  \textsf{rvs}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}\;\overline{ is}  

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_s \mapsto_{r}\{q\}  \textsf{rvs}   \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{rvs} \}

@@

\inferrule[WriteToRegCtlFromReg | \{\textsf{rtv}\} / \{\textsf{rvs}\}]{

@@

\inferrule[WriteToRegFromRegCtl | \{\textsf{rtv}\}]{
